### 2019-08-13 index.Rmd
Fixed Umlaut
Update 0.1-4

@@

<p id="gruen2007">
Gr\"un B, Leisch F (2007).
Fitting Finite Mixtures of Generalized Linear Regressions in _R_.
_Computational Statistics \& Data Analysis_, **51**(11),
doi:<a href="https://dx.doi.org/10.1016/j.csda.2006.08.014" target="_blank">10.1016/j.csda.2006.08.014</a>
</p>

>>>>

# foehnix

[![Build Status](https://api.travis-ci.org/retostauffer/Rfoehnix.svg?branch=master)](https://api.travis-ci.org/retostauffer/Rfoehnix.svg?branch=master)
[![codecov](https://codecov.io/gh/retostauffer/Rfoehnix/branch/master/graph/badge.svg)](https://codecov.io/gh/retostauffer/Rfoehnix)
[![Python](https://img.shields.io/badge/Python-githubio-yellowgreen)](https://matthiasdusch.github.io/foehnix-python/_build/html/)

@@

<p id="gruen2007">
Gr&uuml;n B, Leisch F (2007).
Fitting Finite Mixtures of Generalized Linear Regressions in _R_.
_Computational Statistics \& Data Analysis_, **51**(11),
doi:<a href="https://dx.doi.org/10.1016/j.csda.2006.08.014" target="_blank">10.1016/j.csda.2006.08.014</a>
</p>
